\documentclass[12pt,letterpaper]{book}
\usepackage[top=2.5cm,bottom=2.5cm,left=3.5cm,right=2.5cm]{geometry}
\linespread{1.3}
\setlength{\parindent}{0pt}
\usepackage{epigraph}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{textcomp}
\usepackage{subfigure}
\usepackage{amsfonts}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage{appendix}
\usepackage[pdftex]{graphicx}
\usepackage{makeidx}
\usepackage{natbib}
\usepackage{algorithmic}
\usepackage{listings}

\setlength\fboxsep{0pt}
\setlength\fboxrule{0.5pt}  
\providecommand{\abs}[1]{\left\lvert#1\right\rvert}
\providecommand{\norm}[1]{\left\lVert#1\right\rVert}
\providecommand{\Real}[1]{\mathfrak{Re}\left(#1\right)}
\providecommand{\Imag}[1]{\mathfrak{Im}\left(#1\right)}

\theoremstyle{definition} \newtheorem{definition}{Definición}[section]
\theoremstyle{plain} \newtheorem{theorem}{Teorema}[section]
\theoremstyle{plain} \newtheorem{lemma}{Lema}[section]
\theoremstyle{plain} \newtheorem{proposition}[theorem]{Proposici\'on}
\theoremstyle{plain} \newtheorem{corollary}[theorem]{Corolario}
\theoremstyle{plain} \newtheorem{remark}[theorem]{Comentario}
\newenvironment{example}[1][Ejemplo]{\begin{trivlist}\item[\hskip 
\labelsep {\bfseries #1}]}{\end{trivlist}}
\newenvironment{dedication}
{
   \cleardoublepage
   \thispagestyle{empty}
   \vspace*{\stretch{2}}
   \hfill\begin{minipage}
        [t]{.3\textwidth}
            \raggedright
}
{\end{minipage}
   \vspace*{\stretch{3}}
   \clearpage
}
\newenvironment{acknowledgments}
{
   \cleardoublepage
   \thispagestyle{empty}
}
{
   \clearpage
}
\makeindex

\setlength{\parindent}{15pt}
\author{Amaury Guti\'errez}
\title{Thesis}

\begin{document}

\frontmatter
\include{src/title} 
\include{src/dedications}
\include{src/acknowledgments}

\frontmatter
\tableofcontents
\chapter{Preface}
\input{src/preface}

\mainmatter

\chapter{Motivation}
\epigraph{Good work is not done by `humble' men. (...) A man's first duty, a young man's at any rate, is to be ambitious.}{A Mathematician's Apology \\ G. H. Hardy}
\input{src/chapter-1}

\chapter{Nothing new under the sun}
\epigraph{If I have seen further it is by standing on the shoulders of giants.}{Letter from Sir Isaac Newton to Robert Hooke}
\input{src/chapter-2}

\chapter{Reinventing the wheel}
\epigraph{We may say, roughly, that a mathematical idea is `significant' if it can be connectted, in a natural and illuminating way, with a large complex of other mathematical ideas.}{A Mathematician's Apology \\ G. H. Hardy}
\input{src/chapter-3}

\chapter{Architecture}
\epigraph{A mathematical proof should resemble a simple and clear-cut constellation, not a scattered cluster in the Milky Way.}{A Mathematician's Apology \\ G. H. Hardy}
\input{src/chapter-4}

\chapter{Results}
\epigraph{A mathematican, like a painter or a poet, is a maker of patterns. The mathematician's patterns, like painter's or the poet's, must be \emph{beautiful}; the ideas, like the colours or the words, must fit together in a harmonious way.}{A Mathematician's Apology \\ G. H. Hardy}
\input{src/chapter-5}

\chapter{Future work}
\epigraph{If intellectual curiosity, professional pride, and ambition are the dominant incentives to research, then assuderedly no one has a fairer chance of gratifying them than a mathematician.}{A Mathematician's Apology \\ G. H. Hardy}
\input{src/chapter-6}

\iffalse

\chapter{Some catchy name}
\epigraph{(...) it is obvious that irrationals are uninteresting to an engineer, since he is concerned only with aproximations, and all approximations are rational.}{A Mathematician's Apology \\ G. H. Hardy}
\input{src/chapter-7}

\chapter{Some catchy name}
\epigraph{I believe that mathematical reality lies outside us, that our function is to discover or \emph{observe} it, and that the theorems which we prove, and which we describe grandiloquently as our `creations', are simply our notes of our observations.}{A Mathematician's Apology \\ G. H. Hardy}
\input{src/chapter-8}
\backmatter
\appendix
\chapter{Appendix A}
\input{src/appendix-a}
\chapter{Appendix B}
\input{src/appendix-a}
\chapter{Appendix C}
\input{src/appendix-a}

\fi

\cleardoublepage
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{plain}
\bibliography{src/bibliography}
\cleardoublepage
\printindex

\end{document}
